Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-05-17 scripts/MouseSexDiffApril20_2020.Rmd
some minor changes (not knitting!)

---
title: "Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair
  Senior & Shinichi Nakagawa
date: "April 2020"
output:
  html_document:
    code_download: yes
    code_folding: hide
    depth: 4
    number_sections: no
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    toc: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

```{r packages}
library(pacman)
pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here)
```

@@

```{r Session}
sessionInfo()
```

>>>>

---
title: "Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Alistair
  Senior Daniel Noble, , & Shinichi Nakagawa
date: "April 2020"
output:
  html_document:
    code_download: yes
    code_folding: hide
    depth: 4
    number_sections: no
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    toc: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

```{r packages}
library(pacman)
pacman::p_load(readr, dplyr, metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, pander)
```

@@

```{r}
sessionInfo() %>% pander()
```
